---
title: "Untitled"
author: "Michal Dzwolak"
date: "19 December 2017"
output:
  html_document:
    df_print: paged
---

# Statistical Inference Course Project 2

### Basic Inferential Data Analysis Instructions.

The second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package. 

1. Load the ToothGrowth data and perform some basic exploratory data analyses

2. Provide a basic summary of the data.

3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

4. State your conclusions and the assumptions needed for your conclusions.

####Load the ToothGrowth data and perform some basic exploratory data analyses

```{r load, warning=FALSE, message=FALSE}
library(ggplot2)

upl = ToothGrowth

str(upl)
head(upl)
is.data.frame(upl)

ggplot(data = upl, aes(upl$len), fill=upl$supp) + geom_histogram(alpha=0.5, color = "black") +
  facet_wrap(~upl$supp, ncol = 2, scales = "free") + 
  theme_light() + 
  ggtitle("ToothGrowth Histogram") + 
  xlab('Len')
```

####Provide a basic summary of the data.
```{r summ}
summary(upl)
```

####Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.

T-test based on supp
```{r supp}
levels(upl$supp)
t.test(upl$len[upl$supp=="OJ"], upl$len[upl$supp=="VC"], paired = FALSE)
```

####Conclusion:

As we can see p-value is above significance level 0.05 (0.06063). This is not enugh to reject zero hypotesis. it means supplement type does not influence on Tooth Growth in Guinea Pigs.

T-test based on dose increase from 0.5 to 2
```{r dose1}
range(upl$dose)
t.test(upl$len[upl$dose==0.5], upl$len[upl$dose==2], paired = FALSE)
```

####Conclusion: 

p-value is far below significance level 0.05. It means increase dose levels of vitamin C form 0.5 to 2 has a positive effect on Tooth Growth in Guinea Pigs. Hypothesis zero can not be rejected. 

T-test based on dose increase from 0.5 to 1
```{r dose2}
range(upl$dose)
t.test(upl$len[upl$dose==0.5], upl$len[upl$dose==1], paired = FALSE)
```

####Conclusion: 

p-value is far below significance level 0.05. It means increase dose levels of vitamin C form 0.5 to 1 has a positive effect on Tooth Growth in Guinea Pigs. Hypothesis zero can not be rejected. 

T-test based on dose increase from 1 to 2
```{r dose3}
range(upl$dose)
t.test(upl$len[upl$dose==0.5], upl$len[upl$dose==1], paired = FALSE)
```

####Conclusion: 

p-value is far below significance level 0.05. It means increase dose levels of vitamin C form 1 to 2 has a positive effect on Tooth Growth in Guinea Pigs. Hypothesis zero can not be rejected. 

###Final conclusion

